### 2016-03-15 paper/abstract.tex

\begin{abstract}
This paper proposes a novel MAP inference framework for Markov Random
Field (MRF) in parallel computing environments.  The inference
framework, dubbed Swarm Fusion, is a natural generalization of the
Fusion Move method. Every thread (in a case of multi-threading
environments) maintains and updates a solution. At every iteration, a
thread can generate arbitrary number of solution proposals and take
arbitrary number of concurrent solutions from the other threads to
perform multi-way fusion in updating its solution. The framework is
general, making popular existing inference techniques such as
alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
fusion, its special cases. We have evaluated the effectiveness of our
approach against competing methods on three problems of varying
difficulties, in particular, the stereo, the optical flow, and the
layered depthmap estimation problems.
%Our experiments have shown that the Swarm Fusion method outperform
%competing methods, especially for challenging problems with massive
%solution space.
% can effectively exploits the parallel computing resources and become
%effective especially for challenging problems.
%\yasu{must be at least 70 and at most 150 words.}
\keywords{MRF; Fusion Move; Particle Swarm Optimization}
\end{abstract}

>>>>

\begin{abstract}
This paper proposes a novel MAP inference framework for Markov Random
Field (MRF) in parallel computing environments.  The inference
framework, dubbed Swarm Fusion, is a natural generalization of the
Fusion Move method. Every thread (in a case of multi-threading
environments) maintains and updates a solution. At every iteration, a
thread can generate arbitrary number of solution proposals and take
arbitrary number of concurrent solutions from the other threads to
perform multi-way fusion in updating its solution. The framework is
general, making popular existing inference techniques such as
alpha-expansion, fusion move, parallel alpha-expansion, and hierarchical
fusion, its special cases. We have evaluated the effectiveness of our
approach against competing methods on three problems of varying
difficulties, in particular, the stereo, the optical flow, and the
layered depthmap estimation problems.
%Our experiments have shown that the Swarm Fusion method outperform
%competing methods, especially for challenging problems with massive
%solution space.
% can effectively exploits the parallel computing resources and become
%effective especially for challenging problems.
%\yasu{must be at least 70 and at most 150 words.}
\keywords{MRF; Fusion Move; Particle Swarm Optimization}
\end{abstract}

### 2016-03-15 paper/introduction.tex

Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores, while nowadays most processors have
multiple cores, often 4 or even 8. Cluster computing further expands
the potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on the AI program playing the ancient Chinese board
game of {\it Go}, parallelization plays a key role in the Monte-Carlo
tree search~\cite{silver2016mastering}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
panoramas~\cite{kopf2007capturing}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{hane2013joint}.
%
%% However, state-of-the-art algorithms are still inherently
%% sequential in many Computer Vision problems. Take a Fusion Move
%% method
%% (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
%% for example, which has been one of the most effective techniques
%% for Markov Ran- dom Field (MRF) inference, including the above
%% problems like image denoising, image stitching, or volumetric
%% reconstruction. It sequentially improves solution by fusing the
%% current solution with a solution proposal. Its successful applica-
%% tions go beyond and also cover optical flow, stereo, image
%% inpainting, or image segmentation
%% problems~\cite{fusion_moves_for_markov_random_field_optimization} .
%
The MAP framework, which can be formulated as a Markov Random Field
(MRF) in many low-level Computer Vision problems, provides a universal
and powerful way to solve these problems. However, state-of-the-art
algorithms for MRF inference are still inherently sequential. Take a
Fusion Move method
(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
for example, which has been one of the most effective techniques for
MRF inference, it sequentially improves solution by fusing the current solution with
a solution proposal. Its successful applications cover not only above
problems, but also popular problems like optical flow, stereo, image
inpainting, or image segmentation
problems~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
%
%Our idea is very simple. We believe that the method is easily
%reproducible with minimal coding
%
We believe that the method can be integrated into existing algorithms
with minimal coding, and would have immediate impact on numerous
Computer Vision researchers or engineers.

>>>>

Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores, while nowadays processors with 4 or
8 cores are commonly used. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on the AI program playing the ancient Chinese board
game of {\it Go}, parallelization plays a key role in the Monte-Carlo
tree search~\cite{silver2016mastering}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
panoramas~\cite{kopf2007capturing}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{hane2013joint}.
%
%% However, state-of-the-art algorithms are still inherently
%% sequential in many Computer Vision problems. Take a Fusion Move
%% method
%% (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
%% for example, which has been one of the most effective techniques
%% for Markov Ran- dom Field (MRF) inference, including the above
%% problems like image denoising, image stitching, or volumetric
%% reconstruction. It sequentially improves solution by fusing the
%% current solution with a solution proposal. Its successful applica-
%% tions go beyond and also cover optical flow, stereo, image
%% inpainting, or image segmentation
%% problems~\cite{fusion_moves_for_markov_random_field_optimization} .
%
Markov Random Field (MRF) provides a universal and powerful way to
solve many low-level Computer Vision problems. However,
state-of-the-art algorithms for MRF inference are still inherently
sequential. Take a Fusion Move method
(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
for example, which has been one of the most effective techniques for
MRF inference. It sequentially improves solution by fusing the current
solution with a solution proposal. Its successful applications cover
not only above problems, but also popular problems like optical flow,
stereo, image inpainting, or image segmentation
problems~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
%
%Our idea is very simple. We believe that the method is easily
%reproducible with minimal coding
%
We believe that the method can be integrated into existing algorithms
with minimal coding, and would have immediate benefit to numerous
Computer Vision researchers or engineers.

### 2016-03-15 paper/optical_flow.tex

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}, but
%instead of the HS algorithm, we
use more recent Farneback algorithm with some modifications.~\footnote{First, we
change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
parameter ``polyN''. Besides the clustering idea, we add three simple
proposal generation schemes based on the current solution as suggested
in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
current solution is shifted in either x or y directions for
either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
shifted by a vector randomly drawn from a Gaussian distribution. In
\textit{perturb proposal}, each flow value in the field is
independently shifted by a vector randomly drawn from a Gaussian
distribution. We choose schemes randomly when generating proposals.}

@@

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for four
iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
in one iteration. This pattern is repeated. For SF-SS, each thread
generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for four
iterations and ($\alpha=0, \beta=3$) for one iteration.
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
solve the optical flow problem.
% Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and use images from the Middlebury optical
flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
generation schemes with Lempitsky et al~\cite{fusion_flow}
%instead of the HS algorithm, we
 with some modifications.~\footnote{First, we use more recent
   Farneback algorithm and change the level of pyramids from 1 to 5,
   then use either 3, 5 or 7 for parameter ``polyN''. Besides the
   clustering idea, we add three simple proposal generation schemes
   based on the current solution as suggested in
   \cite{fusion_flow}. In \textit{shift proposal}, the flow field in
   the current solution is shifted in either x or y directions for
   either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow
   field is shifted by a vector randomly drawn from a Gaussian
   distribution. In \textit{perturb proposal}, each flow value in the
   field is independently shifted by a vector randomly drawn from a
   Gaussian distribution. We choose schemes randomly when generating
   proposals.}

@@

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS,
SF) have been evaluated against the competing methods. For SF-MF, each
thread repeats generating solution proposals ($\alpha=1, \beta=0$) for
four iterations and fuses with one solution from others ($\alpha=0,
\beta=1$) in one iteration. This pattern is repeated. For SF-SS, each
thread generates three solution proposals for fusion in each iteration
($\alpha=3$, $\beta=0$). For SF, we repeat the pattern of four
iterations with ($\alpha=3, \beta=0$) plus one iteration with ($\alpha=0,
\beta=3$).
%%
%Note that we have used the same set of proposal generation schemes as
%the competing methods.
We have used TRW-S for multi-way fusion and QPBO for binary fusion.
% , while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
%
% 2 k-way 1 solution sharing. \chen{?}

### 2016-03-15 paper/result_stereo.tex

%One unusual outcome is that Sequential Alpha Expansion and Parallel
%Alpha Expansion (PAE) have the same convergence speed, indicating that
%the stereo problem is a very easy one.
PAE and SF-MF converges faster than the single thread AE. However, the
speedup is not significant, which confirms the fact that the problem
is an easy one.
%This is well known in a community and this fact was rather expected.
Our approaches with multi-way fusion (SF-SS or SF) are the slowest
kind, because the TRW-S for multi-way fusion is slower than multiple
Alpha Expansion steps, and this stereo problem is too easy to gain
benefits through mulit-way fusion. HF doesn't perform well either
because for nodes with two non-leaf children, the algorithm has to
perform QPBO.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Fig. \ref{fig:stereo_threads} shows the energy plot per thread for
SF-MF (ours) and PAE. With solution sharing, the energy of a single
thread in SF-MF decreases more uniformly, while in PAE the energy
makes dramatic decrease at the final fusion.
%
%The graph for PAE again confirms that the
%stereo is an easy problem, because all the threads are quickly
%converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.

\begin{figure}[!h]
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{figure/stereo_thread_pae.png}
\caption{}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{figure/stereo_thread_sf.png}
\caption{}
\end{subfigure}
\caption{Energy plots per thread for the stereo proble for (a) PAE and (b)
SF-MF.}
\label{fig:stereo_threads}
\end{figure}

>>>>

%One unusual outcome is that Sequential Alpha Expansion and Parallel
%Alpha Expansion (PAE) have the same convergence speed, indicating that
%the stereo problem is a very easy one.
PAE and SF-MF converges faster than the single thread AE. However, the
speedup is not significant, which confirms the fact that the problem
is an easy one.
%This is well known in a community and this fact was rather expected.
Our approaches with multi-way fusion (SF-SS or SF) are the slowest
kind, because the TRW-S for multi-way fusion is slower than multiple
Alpha Expansion steps, and this stereo problem is too easy to gain
benefits through mulit-way fusion. HF doesn't perform well because the
algorithm has to perform QPBO for all nodes with two non-leaf
children.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Fig. \ref{fig:stereo_threads} shows the energy plot per thread for
SF-MF (ours) and PAE. With solution sharing, the energy in SF-MF
decreases more uniformly, while in PAE the energy makes dramatic
decrease at the final fusion.
%
%The graph for PAE again confirms that the
%stereo is an easy problem, because all the threads are quickly
%converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.

\begin{figure}[!h]
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{figure/stereo_thread_pae.png}
\caption{}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{figure/stereo_thread_sf.png}
\caption{}
\end{subfigure}
\caption{Energy plots per thread for the stereo problem for (a) PAE and (b)
SF-MF.}
\label{fig:stereo_threads}
\end{figure}
